Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2025-02-07 paper/main.tex
updates

As both PC and Hill-Climb Search can only give us a CPDAG, we

we use simulated data from
a known DAG and compare how well the algorithm is able to recover the original
model using two metrics: Structural Hamming Distance (SHD) and Structural
Intervention Distance (SID). To simulate the data, we start with a randomly
generated DAG on $ 10 $ nodes and use linear models with random effects to
generate the data.

We vary the edge probability of the DAG to generate DAGs with varying density.
We repeat the data generation $ 30 $ times for each density value for the DAG.
As both PC and Hill-Climb Search can only give us a CPDAG, we compare the
orientation of these CPDAG which result in the best and worst case scores on
SHD and SID.

>>>>

As the automated algorithms can only recover the CPDAG from data, and our method
recovers the DAG. To compare them fairly, we computed the SHD and SID for all
possible orientations of the CPDAG and show them in the Figure.
